\documentclass[oneside,english]{amsbook}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{verbatim}
\usepackage{refstyle}
\usepackage{float}
\usepackage{mathrsfs}
\usepackage{tipa}
\usepackage{tipx}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{esint}
\usepackage[authoryear]{natbib}

\makeatletter


\AtBeginDocument{\providecommand\enuref[1]{\ref{enu:#1}}}
\AtBeginDocument{\providecommand\thmref[1]{\ref{thm:#1}}}
\AtBeginDocument{\providecommand\eqref[1]{\ref{eq:#1}}}
\AtBeginDocument{\providecommand\lemref[1]{\ref{lem:#1}}}
\floatstyle{ruled}
\newfloat{algorithm}{tbp}{loa}
\providecommand{\algorithmname}{Algorithm}
\floatname{algorithm}{\protect\algorithmname}
\RS@ifundefined{subref}
  {\def\RSsubtxt{section~}\newref{sub}{name = \RSsubtxt}}
  {}
\RS@ifundefined{thmref}
  {\def\RSthmtxt{theorem~}\newref{thm}{name = \RSthmtxt}}
  {}
\RS@ifundefined{lemref}
  {\def\RSlemtxt{lemma~}\newref{lem}{name = \RSlemtxt}}
  {}


\numberwithin{section}{chapter}
\numberwithin{equation}{section}
\numberwithin{figure}{section}
  \theoremstyle{plain}
  \newtheorem{lem}{\protect\lemmaname}
  \theoremstyle{plain}
  \newtheorem{assumption}{\protect\assumptionname}
  \theoremstyle{definition}
  \newtheorem{defn}{\protect\definitionname}
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
  \theoremstyle{plain}
  \newtheorem{cor}{\protect\corollaryname}
  \theoremstyle{remark}
  \newtheorem{rem}{\protect\remarkname}
 \theoremstyle{definition}
  \newtheorem{example}{\protect\examplename}
  
  \newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\newtheorem{remark}{Remark}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.

\usepackage{verbatim}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Lp}[1][p]{\mathcal{L}_{#1}}
\newcommand{\diff}{\,\mathrm{d}}
\newcommand{\iid}{\mathrm{iid}\,}
\newcommand{\ascv}{\,\mathrm{a.s.}\,}
\newcommand{\Xitn}[2][X]{{#1}_1 \mathrm{,} \ldots \mathrm{,} {#1}_{#2}}
\newcommand{\convdist}[1][d]{\overset{#1}{\rightarrow}}
\renewcommand{\labelenumii}{(\roman{enumii})}
\renewcommand{\labelenumi}{\arabic{enumi}}
 \newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\bibpunct{(}{)}{;}{a}{,}{;}

\makeatother

\usepackage{babel}
  \providecommand{\assumptionname}{Assumption}
  \providecommand{\definitionname}{Definition}
  \providecommand{\examplename}{Example}
  \providecommand{\lemmaname}{Lemma}
  \providecommand{\remarkname}{Remark}
\providecommand{\corollaryname}{Corollary}
\providecommand{\theoremname}{Theorem}

\begin{document}



\include{litRev}

\include{belUni}

\include{belMul}

\include{elOptPrice}

\include{abcsdr}

\appendix
\begingroup 
\let\clearpage\relax 
% command \begingroup \let\clearpage\relax \endgroup shut down the clearpage before \include 
\include{proofBelUni}
\endgroup

\include{proofBelMul}
\include{proofABCSDR}

\chapter*{Reference}

\bibliographystyle{elsarticle-harv}
\bibliography{dissertation,partialPostBib,asymExpBib}
\bigskip
\par\noindent\hangindent2.3em\hangafter 1
Ait-Sahalia, Y. (1996). Nonparametric Pricing of Interest Rate Derivative Securities. {\em Econometrica}, 64(3), 527-560.

\par\noindent\hangindent2.3em\hangafter 1
Ait-Sahalia, Y., \& Lo, A. W. (1998). Nonparametric estimation of state-price densities implicit in financial asset prices. {\em The Journal of Finance}, 53(2), 499-547.

\par\noindent\hangindent2.3em\hangafter 1
Bakshi, G., Cao, C., \& Chen, Z. (1997). Empirical performance of alternative option pricing models. {\em The Journal of Finance}, 52(5), 2003-2049.

\par\noindent\hangindent2.3em\hangafter 1
Bakshi, G., \& Madan, D. (2000). Spanning and derivative-security valuation. {\em Journal of Financial Economics}, 55(2), 205-238.

\par\noindent\hangindent2.3em\hangafter 1
Bates, D. S. (1996). Jumps and stochastic volatility: Exchange rate processes implicit in deutsche mark options. {\em Review of Financial Studies}, 9(1), 69-107.

\par\noindent\hangindent2.3em\hangafter 1
Black, F., \& Scholes, M. (1973). The pricing of options and corporate liabilities. {\em The Journal of Political Economy}, 637-654.

\par\noindent\hangindent2.3em\hangafter 1
Carr, P., \& Madan, D. (1999). Option valuation using the fast Fourier transform. {\em Journal of Computational Finance}, 2(4), 61-73.

\par\noindent\hangindent2.3em\hangafter 1
Carr, P., \& Madan, D. (2009). Saddlepoint methods for option pricing. {\em Journal of Computational Finance}, 13(1), 49.

\par\noindent\hangindent2.3em\hangafter 1
Chan, N. H., \& Ling, S. (2006). Empirical likelihood for GARCH models. {\em Econometric Theory}, 22(03), 403-428.

\par\noindent\hangindent2.3em\hangafter 1
Chuang, C. S., \& Chan, N. H. (2002). Empirical likelihood for autoregressive models, with applications to unstable time series. {\em Statistica Sinica}, 12(2), 387-408.

\par\noindent\hangindent2.3em\hangafter 1
Diciccio, T. J., \& Romano, J. P. (1989). On adjustments based on the signed root of the empirical likelihood ratio statistic. {\em Biometrika}, 76(3), 447-456.

\par\noindent\hangindent2.3em\hangafter 1
Duan, J. C. (1995). The GARCH option pricing model. {\em Mathematical Finance}, 5(1), 13-32.

\par\noindent\hangindent2.3em\hangafter 1
Duffie, D., Pan, J., \& Singleton, K. (2000). Transform analysis and asset pricing for affine jump-diffusions. {\em Econometrica}, 68(6), 1343-1376.

\par\noindent\hangindent2.3em\hangafter 1
Hall, P., \& La Scala, B. (1990). Methodology and algorithms of empirical likelihood. {\em International Statistical Review/Revue Internationale de Statistique}, 109-127.

\par\noindent\hangindent2.3em\hangafter 1
Heston, S. L. (1993). A closed-form solution for options with stochastic volatility with applications to bond and currency options. {\em Review of Financial Studies}, 6(2), 327-343.

\par\noindent\hangindent2.3em\hangafter 1
Heston, S. L., \& Nandi, S. (2000). A closed-form GARCH option valuation model. {\em Review of Financial Studies}, 13(3), 585-625.

\par\noindent\hangindent2.3em\hangafter 1
Huang, C., \& Litzenberger, R. H. (1988). Foundations for financial economics. {\em Princeton University}.

\par\noindent\hangindent2.3em\hangafter 1
Hull, J., \& White, A. (1987). The pricing of options on assets with stochastic volatilities. {\em The Journal of Finance}, 42(2), 281-300.

\par\noindent\hangindent2.3em\hangafter 1
Hutchinson, J. M., Lo, A. W., \& Poggio, T. (1994). A nonparametric approach to pricing and hedging derivative securities via learning networks. {\em The Journal of Finance}, 49(3), 851-889.

\par\noindent\hangindent2.3em\hangafter 1
Kou, S. G. (2002). A jump-diffusion model for option pricing. {\em Management science}, 48(8), 1086-1101.

\par\noindent\hangindent2.3em\hangafter 1
Kitamura, Y. (1997). Empirical likelihood methods with weakly dependent processes. {\em The Annals of Statistics}, 25(5), 2084-2102.

\par\noindent\hangindent2.3em\hangafter 1
Melino, A., \& Turnbull, S. M. (1990). Pricing foreign currency options with stochastic volatility. {\em Journal of Econometrics}, 45(1), 239-265.


\par\noindent\hangindent2.3em\hangafter 1
Merton, R. C. (1980). On estimating the expected return on the market: An exploratory investigation. {\em Journal of Financial Economics}, 8(4), 323-361.

\par\noindent\hangindent2.3em\hangafter 1
Mykland, P. A. (1995). Dual likelihood. {\em The Annals of Statistics}, 396-421.

\par\noindent\hangindent2.3em\hangafter 1
Nordman, D. J., Sibbertsen, P., \& Lahiri, S. N. (2007). Empirical likelihood confidence intervals for the mean of a long-range dependent process. {\em Journal of Time Series Analysis}, 28(4), 576-599.

\par\noindent\hangindent2.3em\hangafter 1
Owen, A. B. (1988). Empirical likelihood ratio confidence intervals for a single functional. {\em Biometrika}, 75(2), 237-249.

\par\noindent\hangindent2.3em\hangafter 1
Owen, A. (1990). Empirical likelihood ratio confidence regions. {\em The Annals of Statistics}, 90-120.

\par\noindent\hangindent2.3em\hangafter 1
Owen, A. B. (2001). Empirical likelihood. {\em CRC press}.

\par\noindent\hangindent2.3em\hangafter 1
Peng, H. (2015) On a class of maximum empirical likelihood estimators. Manuscript



\par\noindent\hangindent2.3em\hangafter 1
Qin, J., \& Lawless, J. (1994). Empirical likelihood and general estimating equations. {\em The Annals of Statistics}, 300-325.

\par\noindent\hangindent2.3em\hangafter 1
Rubinstein, M. (1985). Nonparametric tests of alternative option pricing models using all reported trades and quotes on the 30 most active CBOE option classes from August 23, 1976 through August 31, 1978. {\em The Journal of Finance}, 40(2), 455-480.

\par\noindent\hangindent2.3em\hangafter 1
Scott, L. O. (1987). Option pricing when the variance changes randomly: Theory, estimation, and an application. {\em Journal of Financial and Quantitative Analysis}, 22(04), 419-438.

\par\noindent\hangindent2.3em\hangafter 1
Stutzer, M. (1996). A simple nonparametric approach to derivative security valuation. {\em The Journal of Finance}, 51(5), 1633-1652.

\par\noindent\hangindent2.3em\hangafter 1
Wiggins, J. B. (1987). Option values under stochastic volatility: Theory and empirical estimates. {\em Journal of Financial Economics}, 19(2), 351-372.

\par\noindent\hangindent2.3em\hangafter 1
Yau, C. Y. (2012). Empirical likelihood in long-memory time series models. {\em Journal of Time Series Analysis}, 33(2), 269-275.

\end{document}
